Making all equalities equal

### 2021-09-09 paper.lagda.tex
broke lines

liftIso : ∀ {a b} {A : Type a} {B : Type b} → Iso {a} {b} A B → Iso {ℓ-max a b} {ℓ-max a b} A B
liftIso {a} f = iso fun inv (λ x i → rightInv x i) (λ x i → leftInv x i)
  where open Iso f

>>>>

liftIso : ∀ {a b} {A : Type a} {B : Type b}
  → Iso {a} {b} A B → Iso {ℓ-max a b} {ℓ-max a b} A B
liftIso {a} f = iso fun inv
  (λ x i → rightInv x i) (λ x i → leftInv x i)

  where open Iso f
